---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
commandArgs <- function() { #nolint
  list(
    "--args",
    "a-integer",
    "42",
    "a-float",
    "3.14",
    "a-boolean",
    "FALSE",
    "a-list",
    "1,2,3"
  )
}
```

# W4MRUtils

 - **VERSION**: 1.0.0

<!-- badges: start -->
<!-- badges: end -->

W4MRUtils is a R packages provided by W4M to ease galaxy tools writing.
It contains some utility functions that will help you in common tasks.


## Parameters

 - Parsing parameters with parse_args (easier)
 - Parsing parameters with optparse_parameters (better)
 - Enforce checking on parameters with check_param_type_n_length


## R script chores

 - Silently load a package with shy_lib
 - Sourcing relative file with source_local


## Galaxy

 - Am I in a galaxy env? see in_galaxy_env
 - Show log headers with show_galaxy_header
 - Show log footer with show_galaxy_footer
 - Execute a function with run_galaxy_processing
 - Restore parameters names, modified by galaxy with unmangle_galaxy_param


## Logfiles

 - What is a logger? - See logging section what-is-a-logger)
 - How to create a logger? - See logging section how-to-create-a-logger)
 - How to create a log file? - See logging section how-to-create-a-log-file)


## TODO
Do the documentation and the referencing of the documentation for:

 - stock_id
 - reproduce_id
 - check_err
 - match2
 - match3
 - import2
 - import3
 - df_is
 - df_force_numeric
 - df_read_table


## Installation

You can install the development version of W4MRUtils like so:
```bash
$ git clone https://github.com/workflow4metabolomics/W4MRUtils
$ cd W4MRUtils
```
then

```{bash, install with make, eval=FALSE}
$ make install
```
or
```{r install with R, eval=FALSE}
> rmarkdown::render("README.Rmd")
> devtools::document(".")
> roxygen2::roxygenize(".")
> devtools::test(".")
> devtools::install(".", dependencies = FALSE, repos = NULL, type = "source")
```

or
```{bash install from cran, eval=FALSE}
$ R -q -e "install.packages('W4MRUtils', repos='https://cran.irsn.fr');"
```

## Uninstallation

You can uninstall the version of W4MRUtils you installed with:

```{bash remove with make, eval=FALSE}
$ make remove_package
```
or
```{r remove with R, eval=FALSE}
> remove.packages("W4MRUtils")
```

## XML Wrapper

Please follow [the guidelines](https://galaxy-iuc-standards.readthedocs.io/en/latest/best_practices/tool_xml.html)
during the redaction of the xml wrapper.

Read [the doc](https://docs.galaxyproject.org/en/latest/dev/schema.html)
in case of problems.