---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
commandArgs <- function() {
  list(
    "--args",
    "a-integer",
    "42",
    "a-float",
    "3.14",
    "a-boolean",
    "FALSE",
    "a-list",
    "1,2,3"
  )
}
```

# W4MRUtils

<!-- badges: start -->
<!-- badges: end -->

W4MRUtils is a R packages provided by W4M to ease galaxy tools writing.
It contains some utility functions 

## Installation

You can install the development version of W4MRUtils like so:

```{bash install with make, eval=FALSE}
make install
```
or
```{r install with R, eval=FALSE}
rmarkdown::render("README.Rmd")
devtools::document(".")
roxygen2::roxygenize(".")
devtools::test(".")
devtools::install(".", dependencies = FALSE, repos = NULL, type = "source")
```

## Uninstallation

You can install the development version of W4MRUtils like so:

```{bash remove with make, eval=FALSE}
make remove_package
```
or
```{r remove with R, eval=FALSE}
remove.packages("W4MRUtils")
```


## Example

### parsing parameters

R script command line:
```{sh how to run scritp, eval=FALSE}
Rscript my_script.R --a-integer 42 --a-float 3.14 --a-boolean FALSE --a-list 1,2,3
```
R script content:

```{r example parameters}
param_printer <- function(name, args) {
  cat(sprintf(
    "%s[%s] %s",
    name,
    class(args[[name]])[1],
    paste(args[[name]], collapse = " ")
  ))
}
args <- W4MRUtils::parse_args(commandArgs())
param_printer("a-integer", args)
param_printer("a-float", args)
param_printer("a-boolean", args)
param_printer("a-list", args)
args$`a-list` <- as.numeric(strsplit(args$`a-list`, ",")[[1]])
param_printer("a-list", args)
```


## XML Wrapper

Please follow [the guidelines](https://galaxy-iuc-standards.readthedocs.io/en/latest/best_practices/tool_xml.html)
during the redaction of the xml wrapper.

Read [the doc](https://docs.galaxyproject.org/en/latest/dev/schema.html)
in case of problems.