---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
commandArgs <- function() {
  list(
    "--args",
    "a-integer",
    "42",
    "a-float",
    "3.14",
    "a-boolean",
    "FALSE",
    "a-list",
    "1,2,3"
  )
}
```

# W4MRUtils

<!-- badges: start -->
<!-- badges: end -->

W4MRUtils is a R packages provided by W4M to ease galaxy tools writing.
It contains some utility functions 

## Installation

You can install the development version of W4MRUtils like so:
```bash
$ git clone https://github.com/workflow4metabolomics/W4MRUtils
$ cd W4MRUtils
```
then

```{bash, install with make, eval=FALSE}
$ make install
```
or
```{r install with R, eval=FALSE}
> rmarkdown::render("README.Rmd")
> devtools::document(".")
> roxygen2::roxygenize(".")
> devtools::test(".")
> devtools::install(".", dependencies = FALSE, repos = NULL, type = "source")
```

or
```{bash install from cran, eval=FALSE}
$ R -q -e "install.packages('W4MRUtils', repos='https://cran.irsn.fr');"
```

## Uninstallation

You can uninstall the version of W4MRUtils you installed with:

```{bash remove with make, eval=FALSE}
$ make remove_package
```
or
```{r remove with R, eval=FALSE}
> remove.packages("W4MRUtils")
```

## XML Wrapper

Please follow [the guidelines](https://galaxy-iuc-standards.readthedocs.io/en/latest/best_practices/tool_xml.html)
during the redaction of the xml wrapper.

Read [the doc](https://docs.galaxyproject.org/en/latest/dev/schema.html)
in case of problems.